%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% CV Jakša Tomović 06/2019 %%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\PassOptionsToPackage{dvipsnames}{xcolor}
\documentclass[10pt,a4paper]{altacv}

%Layout
\geometry{left=0.5cm,right=8cm,marginparwidth=7cm,marginparsep=0.5cm,top=0.75cm,bottom=0.75cm,footskip=2\baselineskip}

%Packages
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[default]{lato}
\usepackage{hyperref}

%Colors

\definecolor{accent}{HTML}{000e17}
\definecolor{heading}{HTML}{000e17}
\definecolor{emphasis}{HTML}{696969}
\definecolor{body}{HTML}{01415f}

\colorlet{heading}{heading}
\colorlet{accent}{accent}
\colorlet{emphasis}{emphasis}
\colorlet{body}{body}

\renewcommand{\itemmarker}{{\small\textbullet}}
\renewcommand{\ratingmarker}{\faCircle}

%

\begin{document}
\name{Raul G. Martinez}
\tagline{}
%\photo{2.5cm}{BrunoAlves}
\personalinfo{
    %\printinfo{\faBirthdayCake}{Aug 10th, 1994}
    \email{gio.mtz3@gmail.com}
    \phone{+1 619-734-6231}
%    \mailaddress{SR Njemačke 6, 10000}
    \location{San Diego, CA}
    \linkedin{raul-giovanny-martinez-688b1bb4}
    %\homepage{x}
    \github{github.com/raulgiovannymartinez}
}

%

\begin{fullwidth}
\makecvheader
\end{fullwidth}

%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Experience %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\cvsection[page1sidebar]{Work Experience}

%%%%%%%%%%%%%
%Experience 1
%%%%%%%%%%%%%

\cvevent{Data Engineer, Illumina}{}{July 2018 -- Present}{San Diego, CA}

\begin{itemize}
    % \setlength{\itemindent}{0.5em}
    \item   \small{Developed data integration, ETL, and large-scale analytics for Life-Cycle Management and manufacturing of Next-Generation Sequencing (NGS) platform's test data.}
    % \setlength{\itemindent}{0.5em}
    \item   \small{Configured SQL Server database and performed ad-hoc queries for investigations.}
    % \setlength{\itemindent}{0.5em}
    \item   \small{Executed analytics for investigation and support during the different stages of product development, and functional areas, including optics, hardware, fluidics, software, and chemistry components.}
    % \setlength{\itemindent}{0.5em}
    %\item   \small{Created data pipelines (R, Python, MATLAB) for aggregation, analysis, and visualization (Dashboarding) of NGS instruments data including primary/secondary metrics, engineering tests, reports, and diagnostic logs.}
    % \setlength{\itemindent}{0.5em}
    \item   \small{Innovated algorithms for image processing, manipulation, and transformation using python libraries (i.e. NumPy, PIL).}
\end{itemize}

\medskip

%%%%%%%%%%%%%
%Experience 1.5
%%%%%%%%%%%%%

% \cvevent{Integration Research Associate I-II, Illumina}{}{July 2018 -- July 2020}{San Diego, CA}

% \begin{itemize}
%     \setlength{\itemindent}{0.5em}
%     \item   \small{Collaborated cross-functionally to move forward new integration testing plans (optics,hardware,software, and chemistry components) and Design of Experiments (DOEs) for critical parameter analysis.}
%     \setlength{\itemindent}{0.5em}
%     \item   \small{Implemented data collection strategies with QC targets for NGS instruments in order to monitor optical performance across the fleet over time.}
% \end{itemize}

% \medskip

%%%%%%%%%%%%%
%Experience 3
%%%%%%%%%%%%%

\cvevent{Pharma Technical Development Intern, Genentech/Roche}{}{February 2018 -- July 2018}{South San Francisco, CA}

\begin{itemize}
    % \setlength{\itemindent}{0.5em}
    \item   \small{Contributed with the virology group on process validation and viral clearance studies for the production of therapeutic monoclonal antibodies.}
    % \setlength{\itemindent}{0.5em}
    \item   \small{Investigated virus titers by implementing Design of Experiments (DOEs) and statistical analysis (SAS JMP) for optimizing infectivity assays.}
\end{itemize}

\medskip

%%%%%%%%%%%%%
%Experience 4
%%%%%%%%%%%%%

\cvevent{Support Specialist, Dotmatics}{}{December 2017 -- February 2018}{San Diego, CA}

\begin{itemize}
    % \setlength{\itemindent}{0.5em}
    \item   \small{Collaborated with Developers and Scientists to deliver product suite solutions by testing software UI and querying/updating relational databases.}
\end{itemize}

\medskip

%%%%%%%%%%%%%
%Experience 5
%%%%%%%%%%%%%

\cvevent{Data Analyst, Retrovirox}{}{May 2016 -- July 2017}{San Diego, CA}


\begin{itemize}
%   \setlength{\itemindent}{0.5em}
    \item   \small{Implemented fast turn-around data analysis and workflows for high-throughput screening (FACS Flow Cytometry) of hundreds of novel small-molecules with antiviral activities.}
    % \setlength{\itemindent}{0.5em}
    \item   \small{Facilitated data handling and documentation for R\&D experiments with script automation and by authoring Standard Operating Procedures (SOPs).}
    
\end{itemize}

\medskip

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Projects %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\cvsection[page2sidebar]{Projects and Research}

%%%%%%%%%%%%%
%Project 1
%%%%%%%%%%%%%

\projectevent{PyTorch Deep-Learning Time Series Forecasting Library (2021)}{}{}{}

\begin{itemize}
  \item \small Develop an efficient and user-friendly deep learning open-source library that would benefit the entire PyTorch research community.
    \item \small We will integrate and unify some research code from Dr. Qi (Rose) Yu's lab, and others, in order to include both state of the art research and benchmark reports. 
\end{itemize}

\medskip


%%%%%%%%%%%%%
%Project 2
%%%%%%%%%%%%%

\projectevent{Drug Epidemic Tracking Through Social Media (2020)}{}{}{}

\begin{itemize}
  \item \small Built knowledge graph with Data Integration, NLP, and Entity-Matching strategies such as Blocking, Similarity Functions, Feature Vectors, and ML-Matchers.
    \item \small Consolidated a graph database schema (in Neo4j) to explore drug abuse and overdose patterns, with Cypher declarative queries, across the data ingested from Reddit posts and US News articles. 
\end{itemize}

\medskip

%%%%%%%%%%%%%
%Project 3
%%%%%%%%%%%%%


\projectevent{Predicting Helpfulness of Amazon Reviews (2020)}{}{}{}

\begin{itemize}
  \item \small Analyzed numerical and text data from 200,000 reviews in order to extract useful information with feature engineering and NLP techniques. Feature selection was done with an ablation study. 
    % \setlength{\itemindent}{0.5em}
    \item \small Developed a Random Forest Regressor Model to predict the ratio between the number of helpful votes with total votes, performance metrics used include MAE, MSE, precision, and recall. 
\end{itemize}

\medskip

%\divider

%%%%%%%%%%%%%
%Project 4
%%%%%%%%%%%%%

\projectevent{Identifying Oncogene-Specific Essential Genes (2016)}{}{}{}

\begin{itemize}
  \item \small{Evaluated a bioinformatics prototype using R, based on distributional entropies and kernel-based density estimators to find drug sensitivity profiles that match patterns of gene expression with over 10,000 variables.}
\end{itemize}


\end{document}
