%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% CV Jakša Tomović 06/2019 %%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\PassOptionsToPackage{dvipsnames}{xcolor}
\documentclass[10pt,a4paper]{altacv}

%Layout
\geometry{left=1cm,right=9cm,marginparwidth=6.8cm,marginparsep=1.2cm,top=0.75cm,bottom=0.75cm,footskip=2\baselineskip}

%Packages
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[default]{lato}
\usepackage{hyperref}

%Colors

\definecolor{accent}{HTML}{000e17}
\definecolor{heading}{HTML}{000e17}
\definecolor{emphasis}{HTML}{696969}
\definecolor{body}{HTML}{01415f}

\colorlet{heading}{heading}
\colorlet{accent}{accent}
\colorlet{emphasis}{emphasis}
\colorlet{body}{body}

\renewcommand{\itemmarker}{{\small\textbullet}}
\renewcommand{\ratingmarker}{\faCircle}

%

\begin{document}
\name{Raul G. Martinez}
\tagline{}
%\photo{2.5cm}{BrunoAlves}
\personalinfo{
    %\printinfo{\faBirthdayCake}{Aug 10th, 1994}
    \email{gio.mtz3@gmail.com}
    \phone{+1 619-734-6231}
%    \mailaddress{SR Njemačke 6, 10000}
    \location{San Diego, CA}
    \linkedin{raul-giovanny-martinez-688b1bb4}
    %\homepage{x}
    \github{raulgiovannymartinez}
}

%

\begin{fullwidth}
\makecvheader
\end{fullwidth}

%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Experience %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\cvsection[page1sidebar]{Work Experience}

%%%%%%%%%%%%%
%Experience 1
%%%%%%%%%%%%%

\cvevent{Data Engineer, Illumina}{}{July 2018 -- Present}{San Diego, CA}

\begin{itemize}
    % \setlength{\itemindent}{0.5em}
    \item   \small{Developed data integration strategies, ETL processes, and analytics for manufacturing of Next-Generation Sequencing (NGS) platform's test data.}
    % \setlength{\itemindent}{0.5em}
    \item   \small{Configured SQL Server database and performed ad-hoc queries to gather instruments data for investigation or analysis.}
    % \setlength{\itemindent}{0.5em}
    \item   \small{Executed integration and systems support for NGS platforms during different stages of product development, and functional areas, including optics, hardware, fluidics, software, and chemistry components.}
    % \setlength{\itemindent}{0.5em}
    \item   \small{Created data pipelines (R, Python, MATLAB) for aggregation, analysis, and visualization (Dashboarding) of NGS instruments data including primary/secondary metrics, engineering tests, reports, and diagnostic logs.}
    % \setlength{\itemindent}{0.5em}
    \item   \small{Developed algorithms for image processing, manipulation, and transformation using python libraries (i.e. NumPy, PIL).}
\end{itemize}

\medskip

%%%%%%%%%%%%%
%Experience 1.5
%%%%%%%%%%%%%

% \cvevent{Integration Research Associate I-II, Illumina}{}{July 2018 -- July 2020}{San Diego, CA}

% \begin{itemize}
%     \setlength{\itemindent}{0.5em}
%     \item   \small{Collaborated cross-functionally to move forward new integration testing plans (optics,hardware,software, and chemistry components) and Design of Experiments (DOEs) for critical parameter analysis.}
%     \setlength{\itemindent}{0.5em}
%     \item   \small{Implemented data collection strategies with QC targets for NGS instruments in order to monitor optical performance across the fleet over time.}
% \end{itemize}

% \medskip

%%%%%%%%%%%%%
%Experience 3
%%%%%%%%%%%%%

\cvevent{Pharma Technical Development Intern, Genentech/Roche}{}{February 2018 -- July 2018}{South San Francisco, CA}

\begin{itemize}
    % \setlength{\itemindent}{0.5em}
    \item   \small{Contributed with the virology group on process validation and viral clearance studies for the production of therapeutic monoclonal antibodies.}
    % \setlength{\itemindent}{0.5em}
    \item   \small{Investigated virus titers by implementing Design of Experiments (DOEs) and statistical analysis (SAS JMP) for optimizing infectivity assays.}
\end{itemize}

\medskip

%%%%%%%%%%%%%
%Experience 4
%%%%%%%%%%%%%

\cvevent{Support Specialist, Dotmatics}{}{December 2017 -- February 2018}{San Diego, CA}

\begin{itemize}
    % \setlength{\itemindent}{0.5em}
    \item   \small{Collaborated with Developers and Scientists to deliver product suite solutions by testing software UI and querying/updating relational databases.}
\end{itemize}

\medskip

%%%%%%%%%%%%%
%Experience 5
%%%%%%%%%%%%%

\cvevent{Data Analyst, Retrovirox}{}{May 2016 -- July 2017}{San Diego, CA}


\begin{itemize}
%   \setlength{\itemindent}{0.5em}
    \item   \small{Implemented fast turn-around data analysis and processing workflows for high-throughput screening (with FACS Flow Cytometry) of hundreds of novel small-molecules with antiviral activities.}
    % \setlength{\itemindent}{0.5em}
    \item   \small{Facilitated data handling and documentation (i.e. aggregation, backup and management) for R\&D experiments with script automation and by authoring Standard Operating Procedures (SOPs).}
    
\end{itemize}

\medskip

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Projects %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\cvsection[page2sidebar]{Research and Projects}

%%%%%%%%%%%%%
%Project 1
%%%%%%%%%%%%%

% \cvevent{Non-Invasive Ultrasonic Muscle Force Sensor}{}{September 2016 -- May 2017}{San Diego, CA}

% \begin{itemize}
%   \item \small Analyzed ultrasound wave signals pulsed with small piezoelectric transducers across agar gels with custom Matlab code for waveform feature extraction, LabVIEW simulations, and lab instruments (i.e. Function Gen, Oscilloscope).
% \end{itemize}

\cvevent{Predicting Helpfulness of Amazon Reviews}{}{April 2020 -- Jun 2020}{San Diego, CA}

\begin{itemize}
  \item \small Analyzed numerical and text data from 200,000 reviews in order to extract useful information with feature engineering and NLP techniques. Feature selection was done with an ablation study. 
    % \setlength{\itemindent}{0.5em}
    \item \small Developed a Random Forest Regressor Model to predict the ratio between the number of helpful votes with total votes, performance metrics used include MAE, MSE, precision, and recall. 
\end{itemize}

\medskip

%\divider

%%%%%%%%%%%%%
%Project 2
%%%%%%%%%%%%%

\cvevent{Identifying Oncogene-Specific Essential Genes}{}{January 2016 -- June 2016}{San Diego, CA}

\begin{itemize}
  \item \small{Evaluated a bioinformatics prototype using R language statistical software, based on distributional entropies and kernel-based density estimators to find drug sensitivity profiles that match patterns of gene expression with over 10,000 variables.}
\end{itemize}

%\divider


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Interests %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \cvsection{Interests}

% \wheelchart{1.5cm}{0.5cm}{%
%   10/10em/accent!30/Electronics,
%   25/9em/accent!60/Science,
%   5/13em/accent!10/Movies,
%   20/15em/accent!40/Sport,
%   30/9em/accent/Technology,
%   5/8em/accent!20/Literature
% }


%%New Page
% \clearpage




\end{document}
