%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% CV Jakša Tomović 06/2019 %%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\PassOptionsToPackage{dvipsnames}{xcolor}
\documentclass[10pt,a4paper]{altacv}

%Layout
\geometry{left=0.5cm,right=8cm,marginparwidth=7cm,marginparsep=0.5cm,top=0.75cm,bottom=0.75cm,footskip=2\baselineskip}

%Packages
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[default]{lato}
\usepackage{hyperref}

%Colors

\definecolor{accent}{HTML}{000e17}
\definecolor{heading}{HTML}{000e17}
\definecolor{emphasis}{HTML}{696969}
\definecolor{body}{HTML}{01415f}

\colorlet{heading}{heading}
\colorlet{accent}{accent}
\colorlet{emphasis}{emphasis}
\colorlet{body}{body}

\renewcommand{\itemmarker}{{\small\textbullet}}
\renewcommand{\ratingmarker}{\faCircle}

%

\begin{document}
\name{Raul G. Martinez}
\tagline{}
%\photo{2.5cm}{BrunoAlves}
\personalinfo{
    %\printinfo{\faBirthdayCake}{Aug 10th, 1994}
    \email{gio.mtz3@gmail.com}
    \phone{+1 619-734-6231}
%    \mailaddress{SR Njemačke 6, 10000}
    \location{San Diego, CA}
    \linkedin{raul-giovanny-martinez-688b1bb4}
    %\homepage{x}
    \github{github.com/raulgiovannymartinez}
}

%

\begin{fullwidth}
\makecvheader
\end{fullwidth}

%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Experience %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\cvsection[page1sidebar]{Work Experience}

%%%%%%%%%%%%%
%Experience 1
%%%%%%%%%%%%%

\cvevent{Data Engineer, Illumina}{}{July 2018 -- Present}{San Diego, CA}

\begin{itemize}
    % \setlength{\itemindent}{0.5em}
    \item   \small{Developed data integration, ETL/data pipelines, and data modeling for instrument data (semi-structured, unstructured) across all Next-Generation Sequencing (NGS) platforms with both programming (i.e. python) and application (i.e. alteryx, SQL server) based approaches.}
    % \setlength{\itemindent}{0.5em}
    % \item   \small{Supported relational database systems (SQL server) for storage, transformation, and retrieval.}
    % \setlength{\itemindent}{0.5em}
    \item   \small{Enabled ad hoc analytics for system troubleshooting and root cause investigations for the different NGS core components including optics, hardware, fluidics, software, and chemistry.}
    % \setlength{\itemindent}{0.5em}
    %\item   \small{Created data pipelines (R, Python, MATLAB) for aggregation, analysis, and visualization (Dashboarding) of NGS instruments data including primary/secondary metrics, engineering tests, reports, and diagnostic logs.}
    % \setlength{\itemindent}{0.5em}
    % \item   \small{Innovated algorithms for image processing, manipulation, and transformation using python libraries (i.e. NumPy, PIL).}
\end{itemize}

\medskip

%%%%%%%%%%%%%
%Experience 1.5
%%%%%%%%%%%%%

% \cvevent{Integration Research Associate I-II, Illumina}{}{July 2018 -- July 2020}{San Diego, CA}

% \begin{itemize}
%     \setlength{\itemindent}{0.5em}
%     \item   \small{Collaborated cross-functionally to move forward new integration testing plans (optics,hardware,software, and chemistry components) and Design of Experiments (DOEs) for critical parameter analysis.}
%     \setlength{\itemindent}{0.5em}
%     \item   \small{Implemented data collection strategies with QC targets for NGS instruments in order to monitor optical performance across the fleet over time.}
% \end{itemize}

% \medskip

%%%%%%%%%%%%%
%Experience 3
%%%%%%%%%%%%%

\cvevent{Pharma Technical Development Intern, Genentech/Roche}{}{February 2018 -- July 2018}{South San Francisco, CA}

\begin{itemize}
    % \setlength{\itemindent}{0.5em}
    \item   \small{Collaborated in process development viral clearance studies (i.e. virus removal, inactivation) for the production of therapeutic monoclonal antibodies.}
    % \setlength{\itemindent}{0.5em}
    \item   \small{Investigated and optimized virus titer infectivity assays by implementing design of experiments (using SAS JMP), inferential statistics, and regression analysis.}
\end{itemize}

\medskip

%%%%%%%%%%%%%
%Experience 4
%%%%%%%%%%%%%

\cvevent{Software Support Specialist, Dotmatics}{}{December 2017 -- February 2018}{San Diego, CA}

\begin{itemize}
    % \setlength{\itemindent}{0.5em}
    \item   \small{Collaborated with Software Developers and Application Scientists to deliver scientific informatics product suite solutions by testing software front-end, software architecture, and Oracle relational databases.}
\end{itemize}

\medskip

%%%%%%%%%%%%%
%Experience 5
%%%%%%%%%%%%%

\cvevent{Data Analyst, Retrovirox}{}{May 2016 -- July 2017}{San Diego, CA}


\begin{itemize}
%   \setlength{\itemindent}{0.5em}
    \item   \small{Implemented data analysis and processing workflows for statistical analysis (i.e. linear regression, Z-factor) in high-throughput screening of hundreds of novel small-molecules, using FACS Flow Cytometry techniques, for measuring antiviral activities.}
    % \setlength{\itemindent}{0.5em}
    \item   \small{Executed data management and documentation for R\&D experiments in support to data integrity, reporting, visualization, and experimental design.}
    % \item   \small{Facilitated data handling and documentation for R\&D experiments with script automation and by authoring Standard Operating Procedures (SOPs).}
    
\end{itemize}

\medskip

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Projects %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\cvsection[page2sidebar]{Projects and Research}

%%%%%%%%%%%%%
%Project 1
%%%%%%%%%%%%%

\projectevent{PyTorch Deep-Learning Time Series Forecasting Library (2021)}{}{}{}

\begin{itemize}
  \item \small Develop an efficient and user-friendly deep learning open-source library that would benefit the entire PyTorch research community.
    \item \small We will integrate and unify some research code from Dr. Qi (Rose) Yu's lab, and others, in order to include both state of the art research and benchmark reports. 
\end{itemize}

\medskip


%%%%%%%%%%%%%
%Project 2
%%%%%%%%%%%%%

\projectevent{Drug Epidemic Tracking Through Social Media (2020)}{}{}{}

\begin{itemize}
  \item \small Built knowledge graph with Data Integration, NLP, and Entity-Matching strategies such as Blocking, Similarity Functions, Feature Vectors, and ML-Matchers.
    \item \small Consolidated a graph database schema (in Neo4j) to explore drug abuse and overdose patterns, with Cypher declarative queries, across the data ingested from Reddit posts and US News articles. 
\end{itemize}

\medskip

%%%%%%%%%%%%%
%Project 3
%%%%%%%%%%%%%


\projectevent{Predicting Helpfulness of Amazon Reviews (2020)}{}{}{}

\begin{itemize}
  \item \small Analyzed numerical and text data from 200,000 reviews in order to extract useful information with feature engineering and NLP techniques. Feature selection was done with an ablation study. 
    % \setlength{\itemindent}{0.5em}
    \item \small Developed a Random Forest Regressor Model to predict the ratio between the number of helpful votes with total votes, performance metrics used include MAE, MSE, precision, and recall. 
\end{itemize}

\medskip

%\divider

%%%%%%%%%%%%%
%Project 4
%%%%%%%%%%%%%

\projectevent{Identifying Oncogene-Specific Essential Genes (2016)}{}{}{}

\begin{itemize}
  \item \small{Evaluated a bioinformatics prototype using R, based on distributional entropies and kernel-based density estimators to find drug sensitivity profiles that match patterns of gene expression with over 10,000 variables.}
\end{itemize}


\end{document}
